---
title: "homework4"
author: "yuxin"
date: "2022-10-28"
output: html_document
---
##The task this week is to:

Read in *global gender inequality data*
Join the global gender inequality index to *spatial data of the World*, creating a *new column of difference* in inequality between 2010 and 2019
Share it with the World on GitHub
Add you repository URL to the circulated spreadsheet
Tip：the countrycode R package will be helpful!

Tip：the gender inequality has changed in the last year, you will find what you need in the “All composite indices and components time series (1990-2021)” dataset, the metadata file beneath it will explain what the columns are.
```{r warning=FALSE} 
library(tidyverse)
library(sf)
library(janitor)
library(dplyr)
library(here)
```

```{r warning=FALSE} 
gender_inequality <- read_csv(here::here('data','HDR21-22_Composite_indices_complete_time_series.csv'))
head(gender_inequality)
```

```{r}
gender_inequality_2years <- gender_inequality %>% 
  clean_names() %>% 
  dplyr::select('country','gdi_2010','gdi_2019')
head(gender_inequality_2years)
```

```{r}
worldmap <- st_read(here::here('data','World_Countries_(Generalized)','World_Countries__Generalized_.shp'))
head(worldmap)
```
```{r}
world_inequality <- worldmap %>% 
  merge(.,
        gender_inequality_2years,
        by.x='COUNTRY',
        by.y='country')
head(world_inequality)
```

```{r}
world_inequality_diff <- world_inequality %>% 
  mutate(decade_diff = gdi_2019-gdi_2010)
head(world_inequality_diff)
```
```{r}
world_inequality_diff2 <- world_inequality_diff %>% 
  mutate(diff_type=case_when(decade_diff>0 ~'rise',
                             decade_diff==0 ~'same',
                             TRUE ~'fall'))
```



```{r}
library(tmap)
```

```{r}
tmap_mode('plot')

qtm(world_inequality_diff2,
    fill = 'diff_type')
```







